Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
Add weights section

draft: true
author:  
  # see ?rjournal_article for more information
    - name: John C. Nash
      affiliation: retired professor, University of Ottawa
      address:
      - Telfer School of Management
      - Ottawa ON Canada K1N 6N5
      orcid: 0000-0002-2762-8039
      email: profjcnash@gmail.com
    - name: Arkajyoti Bhattacharjee
      affiliation: Indian Institute of Technology
      address:
      - Department of Mathematics and Statistics
      - Kanpur
      email: arkastat98@gmail.com
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: ../BibSupport/ImproveNLS.bib

---

@@

>>>>

draft: true
author:  
  # see ?rjournal_article for more information
    - name: John C. Nash
      affiliation: retired professor, University of Ottawa
      address:
      - Telfer School of Management
      - Ottawa ON Canada K1N 6N5
      orcid: 0000-0002-2762-8039
      email: profjcnash@gmail.com
    - name: Arkajyoti Bhattacharjee
      affiliation: Indian Institute of Technology
      address:
      - Department of Mathematics and Statistics
      - Kanpur
      email: arkastat98@gmail.com
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: ../BibSupport/ImproveNLS.bib
---

@@

## Feature: Weights on observations

`nls()`, `nlsr::nlxb()` and `minpack.lm::nlsLM()` all have a `weights` argument that
specifies a vector of weights the same length as the number of residuals. Each residual
is multiplied by the square root of the corresponding weight. The values returned by the
`residuals()` function are weighted, and the `fitted()` or `predict()` function are 
used to compute raw residuals.
